Incentivizing Exploration with Unbiased History

### 2018-11-02 intro.tex
minor edit.

\xhdr{Our contributions.}
We start by revisiting the \emph{full-disclosure policy} that reveals the full history of observations from the previous users. We interpret it as the ``gold standard": we posit that users would trust such policy, even if they cannot verify it. Unfortunately, the full-disclosure policy is not good for our purposes, essentially because rational users would \emph{exploit} rather than \emph{explore}. However, for the sake of the argument, what if a disclosure policy reveals the outcomes for every other agent, rather than the outcomes for all agents? We posit that users would trust such policy, too. Given a large volume of data, we posit that users would not be too unhappy with having access to only a fraction this data. A crucial aspect of our intuition here is that the ``subhistory" revealed to a given user comes from a subset of previous users that is chosen in advance, without looking at what happens during the execution. In particular, the subhistory is not ``biased", in the sense that the disclosure policy cannot subsample the observations in favor of a particular action.

With this intuition in mind, we define the class of \emph{unbiased-subhistory policies}: disclosure policies that reveal, to each arriving agent $t$, a subhistory  consisting of the outcomes for a subset $S_t$ of previous agents, where $S_t$ is chosen ahead of time. Further, we impose a transitivity property: if $t' \in S_t$, for some previous agent $t'$, then $S_{t'}\subset S_t$. So, agent $t$ has all information that agent $t'$ had at the time she chose her action. In particular, agent $t$ does not need to second-guess which message has caused aget $t'$ to make choose that action.

>>>>

\xhdr{Our model.}
For the sake of intuition, let us revisit the \emph{full-disclosure policy} that reveals the full history of observations from the previous users. We interpret it as the ``gold standard": we posit that users would trust such policy, even if they cannot verify it. Unfortunately, the full-disclosure policy is not good for our purposes, essentially because rational users would \emph{exploit} rather than \emph{explore}. However, what if a disclosure policy reveals the outcomes for every other agent, rather than the outcomes for all agents? We posit that users would trust such policy, too. Given a large volume of data, we posit that users would not be too unhappy with having access to only a fraction this data. A crucial aspect of our intuition here is that the ``subhistory" revealed to a given user comes from a subset of previous users that is chosen in advance, without looking at what happens during the execution. In particular, the subhistory is not ``biased", in the sense that the disclosure policy cannot subsample the observations in favor of a particular action.

With this intuition in mind, we define the class of \emph{unbiased-subhistory policies}: disclosure policies that reveal, to each arriving agent $t$, a subhistory  consisting of the outcomes for a subset $S_t$ of previous agents, where $S_t$ is chosen ahead of time. Further, we impose a transitivity property: if $t' \in S_t$, for some previous agent $t'$, then $S_{t'}\subset S_t$. So, agent $t$ has all information that agent $t'$ had at the time she chose her action. In particular, agent $t$ does not need to second-guess which message has caused agent $t'$ to make choose that action.
